---
title: "MongoDB with R"
output: html_notebook
---

The purpose of this document is to demonstrate how mongolite performs basic database operations. 


```{r}
library(mongolite)
```


Suppose that we have a simple dataframe. 
```{r}
mg <- mongo(collection = "mydb" , db='kimman',  url = "mongodb://localhost")
mg$drop()
```

#INSERT
## INSERT 1
```{r}
mydata=data.frame(moon=c('titan','europa','enceladus'), planet=c('saturn', 'jupiter','earth'))
mg$insert(mydata)
mg$count()

```
## INSERT 2
```{r}
mg$insert(data.frame(moon=c('moon'), planet=c('earth')))
mg$find()
```




## INSERT 3
This is powerful for MongoDB becuase the schema structure can be easily adjusted. 
```{r}
mg$insert(data.frame(life=c(1), planet=c('earth')))
mg$find()
```

## INSERT 4
```{r}
mg$insert('{ "item": "card", "qty": 15 } ')
mg$find()
```


#UPDATE
This is powerful as we can update a non-existent field
```{r}
mg$update(query=' {"moon":"enceladus"}',  update='{"$set": {"rover":"yes" }} ')
mg$find()
```

```{r}
mg$update(query=' {"moon":"enceladus"}',  update='{"$set": {"rover": {"TYPE":"A", "MASS":"KNOWN"} }} ')
mg$find()
```



#SEARCH
Search with condition (1)
```{r}
mg$find('{"planet" : "earth", "life" : { "$lt" : 5 } }')
```
Search with condition (2)
```{r}

mg$find('{"planet" : "earth", "moon":"moon"}' )
```
Search with condition (3)
```{r}
mg$find('{"rover.TYPE" : "A"}')
df=mg$find('{"rover.TYPE" : "A"}')
print(df)
```



#DELETE
```{r}
mg$remove('{"moon":"titan"}')
mg$find()
```


List out existing database
```{r}
admin <- mongo(db = "admin")
admin$run('{"listDatabases":1}')
```

List out existing collection
```{r}
col <- mongo()
col$run('{"listCollections":1}')
```

Reference
https://jeroen.github.io/mongolite/server-tools.html#running-commands
https://jeroen.github.io/mongolite/calculation.html#aggregate
