---
title: "人工智能知識及應用證書（兼讀制）實習二"
output:
  html_notebook: default
--- 

Date : 01-Oct-2021 v1.1

### Learning Objective
* This tutorial is to demonstrate how to build a more complicated Neural Network model in R<br>
* Students may follow the instructions and gain hands-on experience buiding an AI model. 
* This is a handwritten pattern recognition tutorial.
* By completing the tutorial, students should be able to solve real-world AI problems. 

### Prerequisite
* Students should complete 人工智能知識及應用證書（兼讀制）實習一


```{r}
install.packages('neuralnet')
install.packages('dplyr')
install.packages("remotes")
remotes::install_github('stillmatic/MNIST')
```
Task 1: Install the R Packages
 

```{r}
library(neuralnet)
library(MNIST)
library(dplyr)
```
Task 2: Load the packages <br>
__Question__ What is MNIST? <br>
__Question__ What is dplyr? <br>



```{r}
class(mnist_train)
nrow(mnist_train)
ncol(mnist_train)
head(colnames(mnist_train))
```
Task 3: Exam the raw data <br>
Execute the above. Note that the outcome variable is a factor, which can take on 10 values.<br>
__Question__ Verify that there are 60000 observations, 785 variables, as 784 predictors and 1 outcome variable. 



```{r}
showImage = function(data, row_index){
  #Obtaining the row as a numeric vector
  r = as.numeric(data[row_index, 1:784])

  #Creating a empty matrix to use
  im = matrix(nrow = 28, ncol = 28)

  #Filling properly the data into the matrix
  j = 1
  for(i in 28:1){
    im[,i] = r[j:(j+27)]
    j = j+28
  }  

  #Plotting the image with the label
  image(x = 1:28, 
      y = 1:28, 
      z = im, 
      col=gray((0:255)/255), 
      main = paste("Number:", data[row_index, 'y']))
}
# REF : https://stackoverflow.com/questions/37953644/r-image-plot-mnist-dataset/49483988
```
Task 4: Define a function to show an image <br>
__Question__ What is the size of the image?


```{r}
print(mnist_train[3, ])
```
Task 5: Look at the raw data values <br>
__Question__ What does the three in mnist_train[3, ] mean?<br>
__Question__ What does the zero (the value of V1) mean?<br>


```{r}
showImage(mnist_train, row_index=3)
```
Task 6: Visulalize the data <br>



```{r}
str(mnist_train[3,'V1'])
str(mnist_train[3,'y'])
```
Task 7: int vs Factor<br>
The factor setup is not supported by the neuralnet package, which operates in a matrix framework. 


```{r}
inds <- nnet::class.ind(mnist_train$y)
inds %>% head 
str(inds[3,])
# head(inds) if we do not use pipeline programming technique
```
Task 8: Preparation (Fixing Factor)



```{r}
colnames(inds) <- paste("val", colnames(inds), sep = "")
f <- as.formula(paste(paste(colnames(inds), collapse = "+"), " ~ ", 
                      paste(names(MNIST::mnist_train)[1:784], collapse = "+")))
f
```
Task 9: Preparation 



```{r}
indsdf=data.frame(inds)
trainData = cbind(mnist_train[, 1:784], indsdf)
trainData = trainData %>% sample_frac(0.01)
nrow(trainData)
ncol(trainData)

```
Task 10: Training Data Preparation<br>
__Question__ Explain the meaning of 600 by executing nrow(trainData)?<br>
__Question__ Explain 794 above?<br>

```{r}
colnames(trainData)
```
Task 11: Check the column names<br>


```{r}
model = neuralnet::neuralnet(f, data = trainData, 
                           hidden = 3, linear.output = F)

```
Task 12: Model<br>
__Question__ What is f?<br>
__Question__ How trainData is related to f?<br>
__Question__ What is hidden?<br>
__Question__ Why linear.output is FALSE?<br>


```{r}
plot(model)
```
Task 13: Plot Model<br>
Execute head(model$result.matrix) to obtain the error<br>
__Question__ How could we decrease the neural network error?


```{r}
preds <- neuralnet::compute(model, mnist_test[1, 1:784])
print(mnist_test[1, 'y'])
preds$net.result
```
Task 14: Classify unknown character<br>
__Question__ What is the predicted number?<br>
__Question__ Verify the result by calling showImage?<br>

<br>
<br>
<br>

### Exercises
[1] CRM<br>
Explain how to classify valuable customers from the sales database. Note that each company may keep different data sets. Students should make some assumptions.<br>

[2] Smart ERP<br>
Explain how to neural networks could be adopted to solve inventory replenishment problem.<br> 
Hints: predict the stock movement.<br>

[3] COVID19<br>
```{r}
install.packages("COVID19")
library("COVID19")
usdat=covid19(c("USA"), level = 2)
usDF=data.frame(na.omit(usdat[ , c( 'confirmed', 'recovered', 'deaths')]))
head(usDF)
```

__Question__  Explain the R code above<br>
__Question__  If confirmed=5555 and deaths=333, what could be 'recovered'?<br>


### Reference

[1] MNIST Package<br>
https://rdrr.io/github/stillmatic/MNIST/f/vignettes/neuralnet-mnist.Rmd<br>


